Time series clusters, k = 9

### 2021-04-13 src/ts_clusters_k9.Rmd
online appendix. we need to add some text to make it almost a standalone document.

#test <- 
line2020 <- ts.up2020 %>% 
  mutate(day = recode(weekday, # these are dates from 2020
                            Mon=2,
                            Tue = 3,
                            Wed = 4,
                            Thu = 5,
                            Fri = 6)) %>% 
  mutate(help.date.time = make_datetime(year = 2020, month = 3, day = day),
         hour = paste0(hour, ":00"),
         help.date.time = (as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))) %>% 
  group_by(help.date.time) %>%
  summarise(mean.up = mean(mean.up)) %>% 
  ggplot(aes(x=help.date.time, y=mean.up), #, group = LAD19NM, colour = LAD19NM),
         show.legend = F) + 
  geom_line() + guides(colour=FALSE) +
  xlab(2020)
  # + xlab("Year") +
  # ylab("Pareto exponent")

# library(plotly)
# ggplotly(test,
#          show.legend=F)

@@

# this is the heaviest version:
# (i) directly from the web
#la <- readOGR("http://geoportal1-ons.opendata.arcgis.com/datasets/b6d2e15801de45328b760a4f55d74318_0.geojson?outSR={%22latestWkid%22:3857,%22wkid%22:102100}")#, layer="OGRGeoJSON")
# or, (ii) from the json I saved locally
# path.json <- paste(path, "./data/raw/Local_Authority_Districts_(April_2019)_Boundaries_UK_BFE.geojson", sep = "")
# la <- readOGR(path.json)#, layer="OGRGeoJSON")
# UK BGC: 
la <- readOGR("https://opendata.arcgis.com/datasets/0e07a8196454415eab18c40a54dfbbef_0.geojson")
# UK BFC: la <- readOGR("https://opendata.arcgis.com/datasets/1d78d47c87df4212b79fe2323aae8e08_0.geojson")

# source: https://data.gov.uk/dataset/7c387c64-d25f-474a-b07e-b933578caea2/local-authority-districts-april-2019-boundaries-uk-bfe
# also saved locally \data\raw\Local_Authority_Districts_(December_2019)_Boundaries_UK_BGC.geojson

@@

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  #labs(title = "Upload clusters") +
  scale_fill_brewer(palette="Set1", 
                    direction = -1) +
  geom_text_repel( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=4) +
  geom_point( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="black", size=1) +
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

# Run only if needed
# out.path.map <- paste0(path, "/paper/v2_taylor_francis/figures/map.up.clusters.png")
# ggsave(out.path.map)
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

>>>>

#test <- 
line2020 <- ts.up2020 %>% 
  mutate(day = recode(weekday, # these are dates from 2020
                            Mon=2,
                            Tue = 3,
                            Wed = 4,
                            Thu = 5,
                            Fri = 6)) %>% 
  mutate(help.date.time = make_datetime(year = 2020, month = 3, day = day),
         hour = paste0(hour, ":00"),
         help.date.time = (as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))) %>% 
  group_by(help.date.time) %>%
  summarise(mean.up = mean(mean.up)) %>% 
  ggplot(aes(x=help.date.time, y=mean.up), #, group = LAD19NM, colour = LAD19NM),
         show.legend = F) + 
  geom_line() + guides(colour=FALSE) +
  xlab(2020)

@@

# this is the heaviest version:
# (i) directly from the web
#la <- readOGR("http://geoportal1-ons.opendata.arcgis.com/datasets/b6d2e15801de45328b760a4f55d74318_0.geojson?outSR={%22latestWkid%22:3857,%22wkid%22:102100}")#, layer="OGRGeoJSON")
# or, (ii) from the json I saved locally
# path.json <- paste(path, "./data/raw/Local_Authority_Districts_(April_2019)_Boundaries_UK_BFE.geojson", sep = "")
# la <- readOGR(path.json)#, layer="OGRGeoJSON")

# UK BGC: 
la <- readOGR("https://opendata.arcgis.com/datasets/0e07a8196454415eab18c40a54dfbbef_0.geojson")
# also saved locally \data\raw\Local_Authority_Districts_(December_2019)_Boundaries_UK_BGC.geojson
# source: https://geoportal.statistics.gov.uk/

# fully generalised
#la <- readOGR("https://opendata.arcgis.com/datasets/3a4fa2ce68f642e399b4de07643eeed3_0.geojson")

@@

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  #labs(title = "Upload clusters") +
  scale_fill_brewer(palette="Set1", 
                    direction = -1) +
  geom_text_repel( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=4) +
  geom_point( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="black", size=1) +
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()
```
